---
title: "Book Reading"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
booklist <- read.csv("booklist.csv")
library(ggplot2)
library(dplyr)
library(cowplot)
```

I found I enjoyed the simple process of writing down the books I'd read, which spawned this small effort. I soon set myself a target of reading 24 books annually, and also set a target of reading at least one Pullitzer Prize winning work each year.



### How I'm doing

Three years of steady progress and then a decline. But here's to better trends going forward.

```{r over-time, echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)

by_year <- booklist %>%
  group_by(year) %>%
  summarise(Books = n())

plot_ly(by_year, x = ~year, y = ~Books,
        type = 'scatter', mode = 'lines') %>%
  layout(shapes=list(list(type = 'line', 
                                        x0 = 2016,
                                        x1 = 2022, 
                                        y0 = 24,
                                        y1 = 24, 
                                        line = list(width = 2, dash = "dot"))))


```

### What have I read this year?
```{r current-books, echo=FALSE}
library(reactable)

this_year <- max(booklist$year)

current_year <- booklist %>%
  filter(year == this_year) %>%
  select(Title = long.title,
         Author = author)

reactable(current_year,
          showSortable = TRUE)

```
