---
title: 'Pullitzer Progress'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pullitzer <- read.csv("pullitzer.csv")
library(ggplot2)
library(dplyr)
library(cowplot)
```


Several years ago, I resolved to read more books, but was a bit lost as to how go about it.
I figured award-winning books were a good start, and no better system than the Pulitzer, which
has "History" and "General Non-Fiction" categories that I now try to read from. My goal is to have
read at least one of the finalists each year.


```{r pullitzer-by-year, message=FALSE, warning=FALSE}

pullitzer_years <- pullitzer %>%
  group_by(year, category) %>%
  summarise(count = sum(read))

ggplot(pullitzer_years, aes(x = year, y = count, fill = category)) +
  geom_area() +
  ylim(0,(max(pullitzer_years$count)+1)) +
  theme_minimal()

```

## The full list

These are the finalists and winners of general nonfiction and history, and my progress in reading them.

```{r over-time, echo=FALSE}
library(reactable)
plot_table <- pullitzer %>%
  arrange(desc(year), desc(category), desc(award)) %>%
  select(-long.title)

reactable(plot_table,
          sortable = TRUE,
          showSortable = TRUE,
          defaultPageSize = 20,
          rowStyle = function(index) {
            if (plot_table[index,"read"] == 1) {
              list(fontWeight = "bold")
            }
          })

```